A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-28 manuscript.Rmd
review max's edits

Scientists increasingly strive to make research data, materials, and analysis code openly available.
Sharing these types of digital research artifacts has the potential to increase scientific efficiency by enabling researchers to learn from each other and reuse materials, and to increase scientific reliability by facilitating the review and replication of published research results.
To some extent these potential benefits are contingent on whether these digital research artifacts are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research hinges on its objectivity. Objectivity in this context means "in principle it can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper]. Therefore, reproducibility has long been considered integral to empirical research.
<!---
You tend to use quite long sentences with many subclauses. While this has a long tradition in the german language, it is considered bad style in english. Also it often leads to minor mistakes like dangling modifiers.
-->
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project with all code, data, and materials reproducible comes with a variety of challenges, and there is a dire need for reproducibility standards.
We now have the technology to make all artefacts related to a research project available so that a research project can be reproduced with minimal effort.

@@

Scientific organizations and funding bodies increasingly demand transparent sharing of research artifacts, and researchers are increasingly willing to do so.
<!---
I am not shure about the word artifact in general. Is it common terminology?
-->
However, although the sharing of such artifacts is a necessary condition for reproducibility, it is not a sufficient one.
This was illustrated by an attempt to reproduce results from open materials in the journal *Cognition* [@hardwicke2018]. 
Out of 35 published articles with open research artifacts, results of 22 articles could be reproduced but in 11 of these cases, further assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
Another study of 62 Registered Reports found that only 41 had data available, and 37 had analysis scripts available [@obels2020].
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards, because open repositories do not routinely provide sufficient information to reproduce relevant computational and statistical results.
If research artifacts are available but not reproducible, their added value is limited.

@@

Second, we rely on **dynamic document generation**.
The traditional way of writing a scientific report based on a statistical data analysis uses two separate steps conducted in two different programs.
In a word processor, the researcher writes the text, and in another software, they conduct the analysis.
Typically, results are manually copied and pasted from one software another, a process that often produces inconsistencies [@nuijtenPrevalenceStatisticalReporting2016].

Dynamic document generation integrates both steps.
Through dynamic document generation, code becomes an integral, although usually hidden, part of the manuscript, complementing the verbal description and allows interested readers deeper understanding [@knuthCWEBSystemStructured; @claerboutElectronicDocumentsGive1992].
**R Markdown** uses Markdown for writing the text and R (or other programming languages) for the analysis.
Markdown is a lightweight text format in plain text with a minimal set of reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing.
It is highly fool-proof [unlike, for example, LaTeX @lamportLATEXDocumentPreparation1994], works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest using Markdown for all sorts of documents that are created in the academic context, starting from simple sketches of your ideas, to your scientific manuscripts [@R-rticles] and presentations [@revealjs], or even your résumé [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks [in fact, arbitrary computer code @riedererChapter15Other] into a Markdown document.
Upon rendering the document, the code blocks are executed, and their output is dynamically inserted into the document.
This allows the creation of formatted text, statistical results, and figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).
@xieMarkdownCookbook2020 provides an extensive yet practical introduction to most features of R Markdown.

@@

To automatically resolve dependencies between project files, we rely on **dependency tracking**.
In essence, researchers provide a collection of computational instructions (_recipes_) that describe how ingredients are processed to create intermediate products and, in the end, a final product.
Similar to a collection of cooking recipes, we can have multiple products (_targets_) with different ingredients (_requirements_) and different steps of preparation (_recipes_).
In the context of scientific data analysis, the targets are typically the final scientific report (e.g., the one to be submitted to a journal) and possibly intermediate results (such as preprocessed data files, simulation results, and analysis results).

@@

**Docker** is an example of containerization.
It provides all software used in an analysis, including the operating system itself.
(The operating system level is important because some functionality may be passed to software layers beneath the programming language, for example random number generators and linear algebra libraries.)
Docker does this without interfering with the already installed software by using a virtual software environment independent of the host software environment.
Researchers therefore have the opportunity to use the exact same software setup that was used by the original authors.
Such a snapshot of the software stack is called an "image".
Packaging all required software in such an image requires considerable amounts of storage space.
Two major strategies help to keep the storage requirements reasonable.
One strategy is to rely on pre-made images, which are maintained by a community for particular purposes.
For example, there are pre-made images that only include what is necessary for R, based on Ubuntu (a Linux operating system) containers [@boettigerIntroductionRockerDocker2017].
Users can then install whatever they need in addition to what is provided by these pre-compiled images.
`r ifelse(is.na(container_size), "", glue::glue("The image that was used for this article uses {round(container_size, 2)}Gb of disk space."))`
The image for this project includes Ubuntu, R, R Studio, LaTeX as well as a variety of R packages like the tidyverse [@tidyverse] and all their dependent packages, amounting to `r installed.packages() %>% as.data.frame() %>% filter(is.na(Priority)) %>% nrow()` R packages.
A second strategy is to save a container recipe, a so-called  `Dockerfile` containing a textual description of all commands that need to be executed to recreate the software environment, instead of the software environment itself.
Dockerfiles are tiny (the [Dockerfile](https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile) for this project has a size of only `r round(as.numeric(fs::file_size("Dockerfile"))/1024^1, 2)`Kb).
However, they rely on the assumption that all software repositories that provide the dependent operating systems, pieces of software, and R packages will remain accessible in future and will continue to make available historic software versions.
For proper archival, we therefore recommend storing a complete image of the software environment besides the Dockerfile.
A more comprehensive overview of the use of containarization in research projects is given by @wiebelsLeveragingContainersReproducible2021.

@@

The above mentioned tools require expertise that is beyond the traditional curriculum of researchers.
To aid researchers adopting these tools we rely on and have developed helpers that wrap more complicated (and powerful) tools.
These helpers wrap standard tools but provide feedback about what the computer does and what the user should do in layman's terms and are accessible from within R.
These alternative tools are merely an assistance system, and as users get more and more comfortable, they can use the underlying tools directly to solve more complex problems.

@@

They detect the users' system state and explain if further action is needed.
For example, the following happens if you were a Windows user who does not have Git installed:

@@

For Git to recognize changes to a given file, you have to stage and then commit these changes (this is the basic save action for a project snapshot).
The easiest way to do this is to use the RStudio Git pane.
Click on the empty box next to the file you want to stage, and when a tick appears, which means that the file is staged.
After you have staged all files you would like to, click on the commit button, explain in the commit message why you made those changes, and then click on commit.
<!---
Maybe first click on the commit button and then stage, because in the bigger window you can browse the changes.
-->

@@

The results of your code are dynamically inserted into the document.
Dynamically means that whenever you turn the R Markdown into its output format the code is executed again and if you changed something the results are updated.
<!---
you did not explain how to knit and to choose an output format
-->
The output document is then static, e.g. a pdf document, and can be shared wherever you like, e.g on a preprint server.
This static document is somewhat decoupled from the R Markdown and the rest of the code that did create it.
It is quite possible that several slightly different versions are therefore circulating.
We therefore recommend to connect the static document to the version control system by dynamically including the identifier of the Git commit, called hash, in the document.
The `repro` package comes with the function `repro::current_hash()` for that purpose.
This document was created from the commit with the hash ``r repro::current_hash()``.

@@

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
<!---
What is consistency?
-->
At this point, we would like to emphasize that a prerequisite for reproducibility is that every step taken in an analysis can be **automatically** reproduced.
This means there must be no manual processing such as copy and pasting, manual modification of data files (e.g., manually removing observations or manually recoding variables). 
Ideally, all data preprocessing is well-documented and gathered in a separate R file, which is then called before a Markdown report is generated (that is, the preprocessing script is added in the metadata header under _scripts:_).

@@

The following section explains how to overcome these limitations while still relying on the automations provided by `repro`.
Lifting these limitations requires the user to interact more directly with Make or Docker.
To satisfy more complicated requirements users need to understand how repro utilizes Make and Docker internally.
<!-- I am pretty shure you are saying that users should satisfy more complicated requirements ^^ -->

@@

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For a priori planned analyses, preregistration should reduce "researcher degrees of freedom", the number of decisions researchers can make that could influence the results.
However, some problems described in the literature make it questionable whether preregistration can achieve its goals.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration is comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
The structure these templates provide can more effectively reduce researcher degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
Nevertheless, these templates can not remove all researcher degrees of freedom because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write and publish the code to conduct the analysis before you gather data.
<!-- I am not shure if it is good to directly talk to the reader in this form -->
We term this *preregistration as code (PAC)*.
PAC has the potential to eliminate all researcher degrees of freedom, even those standard preregistration can not eliminate.

@@

Second, although it has been almost a decade since @steegenMeasuringCrowdAgain2014 have preregistered their code, the idea of publishing code before analyzing data has gained not much traction.
<!-- This is not a reason why PAC and reproducibility are related -->
This could change when combining the here proposed workflow and PAC.
We want to extend PAC from preregistering code to preregistering *the whole manuscript as a dynamic document*.
The idea is as follows:
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
In this document, the results are initially based on simulated data that mimics the expected output.

@@

We believe that pairing PAC with the here presented workflow offers five advantages over classical preregistration.
First, a PAC removes any ambiguity regarding the translation of a verbal analysis plan into code.
Second, while being rigorous, it offers the flexibility to incorporate data-dependent decisions if they can be formulated as code.
Researchers can, for example, formulate conditions under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods or an analysis may perform automated variable selection mechanisms before running the final model.
Third, a PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
We believe PAC reveals missing steps or ambiguous decisions. 
It can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
Fourth, deviations from the preregistration are visible because they are reflected in changes to the code, which are managed and tracked with version control.
Fifth, the preregistration is merely a development stage of the final manuscript, thus sparing authors from writing, and editors and reviewers from evaluating two separate documents.

@@

Leaving meta-scientific benefits aside, a preregistration is also a tool for study planning.
To use PAC for study planning, we suggest that researchers write a dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
To that end, they should borrow from widely employed standards for writing an empirical manuscript [e.g. @apa7].
Then they should translate their method section into executable computer code and simulate data that has the same structure as the data they expect to obtain from their experiments.

@@

With simulated data, researchers can check if the analysis recovers the known parameters of the simulation.
When an analysis fails to recover the correct values in idealized conditions with big samples, researchers should not expect this analysis to be effective under realistic conditions.
Because the simulation captures the researchers' expectations about the real world, it is the best way to assess the effectiveness of the analysis without actually gathering the data.
<!-- I would maybe say something about why the simulated data captures researchers expectations. I think for most people data simulation is a novel topic, and even more so the idea that complicated assumptions about the real world (skewness, factor structure of a test, violated measurement invariance) can be incorporated into the simulation -->

@@

```{r, eval=FALSE}
simulate_data <- function(n, effect_size, measurement_error, etc.){
  # 1. warn users that the results are mocked
  # 2. draw `n` samples with `effect_size`
  # 3. Further assumptions can be passed to this function, like measurement error, skewness, etc.
  # 4. format and return in expected data format
}
```

@@

When the researchers are satisfied with the function `planned_analysis()`, they can think about how they would like to report the analysis results via tables, plots, and text.
The implementation of this reporting should be in the function `report_analysis()`.
<!-- Inconsistent naming of the function report_analysis() !! -->

```{r, eval=FALSE}
report_results <- function(results){
  # 1. create markdown tables from results
  # 2. conditionally interpret results e.g. if(p < .025)"Result is significant."
  # 3. visualize results
  # 4. return results section formatted in markdown
}
```

@@

The interested reader can find the example rendered as a pdf file with actual data in the [online supplementary material](this link does not work) and can view the changes we made since preregistering it on this [GitHub page](this link does not work).
<!-- I would show the rendered PDF (as long as it is shorter than one page) -->

@@

Please note that the statistical procedure in the PAC example of running different test procedures based on a fixed skewness threshold was created for didactic purposes and is not necessarily optimal for addressing your research question.
The t-test and Mann–Whitney–Wilcoxon test are arguably the most often used hypothesis test [@fagerlandTtestsNonparametricTests2012; @hortonStatisticalMethodsJournal2005 reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005].
The analytical strategy presented here is in fact suboptimal with regard to several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions [@stonehouseRobustnessTestsCombined1998]).
<!-- nobody cares about limitations of the example analysis, I would delete all of this -->

>>>>

Scientists increasingly strive to make research data, materials, and analysis code openly available.
Sharing these types of digital research artifacts has the potential to increase scientific efficiency by enabling researchers to learn from each other and reuse materials, and to increase scientific reliability by facilitating the review and replication of published research results.
To some extent these potential benefits are contingent on whether these digital research artifacts are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research hinges on its objectivity. Objectivity in this context means "in principle it can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper].
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project with all code, data, and materials reproducible comes with a variety of challenges, and there is a dire need for reproducibility standards.
We now have the technology to make all artefacts related to a research project available so that a research project can be reproduced with minimal effort.

@@

Scientific organizations and funding bodies increasingly demand transparent sharing of research artifacts, and researchers are increasingly willing to do so.

However, although the sharing of such artifacts is a necessary condition for reproducibility, it is not a sufficient one.
This was illustrated by an attempt to reproduce results from open materials in the journal *Cognition* [@hardwicke2018]. 
Out of 35 published articles with open research artifacts, results of 22 articles could be reproduced but in 11 of these cases, further assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
Another study of 62 Registered Reports found that only 41 had data available, and 37 had analysis scripts available [@obels2020].
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards, because open repositories do not routinely provide sufficient information to reproduce relevant computational and statistical results.
If research artifacts are available but not reproducible, their added value is limited.

@@

Second, we rely on **dynamic document generation**.
The traditional way of writing a scientific report based on a statistical data analysis uses two separate steps conducted in two different programs.
In a word processor, the researcher writes the text, and in another software, they conduct the analysis.
Typically, results are manually copied and pasted from one software to another, a process that often produces inconsistencies [@nuijtenPrevalenceStatisticalReporting2016].

Dynamic document generation integrates both steps.
Through dynamic document generation, code becomes an integral, although usually hidden, part of the manuscript, complementing the verbal description and allows interested readers deeper understanding [@knuthCWEBSystemStructured; @claerboutElectronicDocumentsGive1992].
**R Markdown** uses Markdown for writing the text and R (or other programming languages) for the analysis.
Markdown is a lightweight text format in plain text with a minimal set of reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing.
It is highly fool-proof [unlike, for example, LaTeX @lamportLATEXDocumentPreparation1994], works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest using Markdown for all sorts of documents that are created in the academic context, starting from simple sketches of your ideas, to your scientific manuscripts [@R-rticles] and presentations [@revealjs], or even your résumé [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks [in fact, arbitrary computer code @riedererChapter15Other] into a Markdown document.
Upon rendering the document, the code blocks are executed, and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, and figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).
@xieMarkdownCookbook2020 provides an extensive yet practical introduction to most features of R Markdown.

@@

To automatically resolve dependencies between project files, we rely on **dependency tracking**.
In essence, researchers provide a collection of computational recipes that describe how ingredients are processed to create intermediate products and, in the end, a final product.
Similar to a collection of cooking recipes, we can have multiple products (_targets_) with different ingredients (_requirements_) and different steps of preparation (_recipes_).
In the context of scientific data analysis, the targets are typically the final scientific report (e.g., the one to be submitted to a journal) and possibly intermediate results (such as preprocessed data files, simulation results, and analysis results).

@@

**Docker** is an example of containerization.
It provides all software used in an analysis, including the operating system itself.
The operating system level is important because some functionality may be passed to software layers beneath the programming language, for example random number generators and linear algebra libraries.
Docker does this without interfering with the already installed software by using a virtual software environment independent of the host software environment.
Researchers therefore have the opportunity to use the exact same software setup that was used by the original authors.
Such a snapshot of the software stack is called an "image".
Packaging all required software in such an image requires considerable amounts of storage space.
Two major strategies help to keep the storage requirements reasonable.
One strategy is to rely on pre-made images, which are maintained by a community for particular purposes.
For example, there are pre-made images that only include what is necessary for R, based on Ubuntu (a Linux operating system) containers [@boettigerIntroductionRockerDocker2017].
Users can then install whatever they need in addition to what is provided by these pre-compiled images.
`r ifelse(is.na(container_size), "", glue::glue("The image that was used for this article uses {round(container_size, 2)}Gb of disk space."))`
The image for this project includes Ubuntu, R, R Studio, LaTeX as well as a variety of R packages like the tidyverse [@tidyverse] and all their dependent packages, amounting to `r installed.packages() %>% as.data.frame() %>% filter(is.na(Priority)) %>% nrow()` R packages.
A second strategy is to save a container recipe, a so-called  `Dockerfile` containing a textual description of all commands that need to be executed to recreate the software environment, instead of the software environment itself.
Dockerfiles are tiny (the [Dockerfile](https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile) for this project has a size of only `r round(as.numeric(fs::file_size("Dockerfile"))/1024^1, 2)`Kb).
However, they rely on the assumption that all software repositories that provide the dependent operating systems, pieces of software, and R packages will remain accessible in future and will continue to make available historic software versions.
For proper archival, we therefore recommend storing a complete image of the software environment besides the Dockerfile.
A more comprehensive overview of the use of containarization in research projects is given by @wiebelsLeveragingContainersReproducible2021.

@@

The above mentioned tools require expertise that is beyond the traditional curriculum of researchers.
To aid researchers adopting these tools we rely on and have developed helpers that wrap more complicated (and powerful) tools.
These helpers wrap standard tools but provide feedback about what the computer does and what the user should do in layman's terms and are accessible from within R.
We hope this makes reproducibility tools more accessible by enabling beginner-level users to detect their systems state accurately and act correspondingly [@parasuramanAutomationHumanPerformance2018, Chapter 8: "Automation and Situation Awareness"].
These alternative tools are merely an assistance system, and as users get more and more comfortable, they can use the underlying tools directly to solve more complex problems.

@@

They detect the users' system state and explain if further action is needed.
Sometimes they ask the user to do something, for example, the following happens if you were a Windows user who does not have Git installed:

@@

For Git to recognize changes to a given file, you have to stage and then commit these changes (this is the basic save action for a project snapshot).
The easiest way to do this is to use the RStudio Git pane.
Click on the empty box next to the file you want to stage, and when a tick appears, which means that the file is staged.
After you have staged all files you would like to, click on the commit button, explain in the commit message why you made those changes, and then click on commit.

@@

The results of your code are dynamically inserted into the document.
Dynamically means that whenever you turn the R Markdown into its output format the code is executed again and if you changed something the results are updated.
The output document is then static, e.g. a pdf document, and can be shared wherever you like, e.g on a preprint server.
This static document is somewhat decoupled from the R Markdown and the rest of the code that did create it.
It is quite possible that several slightly different versions are therefore circulating.
We therefore recommend to connect the static document to the version control system by dynamically including the identifier of the Git commit, called hash, in the document.
The `repro` package comes with the function `repro::current_hash()` for that purpose.
This document was created from the commit with the hash ``r repro::current_hash()``.

@@

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
At this point, we would like to emphasize that a prerequisite for reproducibility is that every step taken in an analysis can be **automatically** reproduced.
This means there must be no manual processing such as copy and pasting, manual modification of data files (e.g., manually removing observations or manually recoding variables). 
Ideally, all data preprocessing is well-documented and gathered in a separate R file, which is then called before a Markdown report is generated (that is, the preprocessing script is added in the metadata header under _scripts:_).

@@

The following section explains how to overcome these limitations while still relying on the automations provided by `repro`.
Lifting these limitations requires the user to interact more directly with Make or Docker.
To satisfy more complicated requirements useres may have, they need to understand how `repro` utilizes Make and Docker internally.

@@

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For a priori planned analyses, preregistration should reduce "researcher degrees of freedom" therefore, the number of decisions researcher can make that could unduly influence the results.
Preregistrations, however, have a problem.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration is comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
The structure these templates provide can more effectively reduce researcher degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
Nevertheless, these templates can not remove all researcher degrees of freedom because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write and publish the code to conduct the analysis before you gather data.
We term this *preregistration as code (PAC)*.
PAC has the potential to eliminate all researcher degrees of freedom, even those standard preregistration can not eliminate.

@@

Second, although it has been almost a decade since @steegenMeasuringCrowdAgain2014 have preregistered their code, the idea of publishing code before analyzing data has gained not much traction.
This could change when combining the here proposed workflow and PAC.
We want to extend PAC from preregistering code to preregistering *the whole manuscript as a dynamic document*.
The idea is as follows:
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
In this document, the results are initially based on simulated data that mimics the expected output.

@@

We believe that pairing PAC with the here presented workflow offers five advantages over classical preregistration.
First, a PAC removes any ambiguity regarding the translation of a verbal analysis plan into code.
Second, while being rigorous, it offers the flexibility to incorporate data-dependent decisions if they can be formulated as code.
Researchers can, for example, formulate conditions under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods or an analysis may perform automated variable selection mechanisms before running the final model.
Third, a PAC is more comprehensive by design because its completeness can be checked with simulated data.
Using simulated data makes it straightforward to detect missing steps or ambiguous decisions.
Because of its strict structure, PAC can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
It can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
Fourth, deviations from the preregistration are visible because they are reflected in changes to the code, which are managed and tracked with version control.
Fifth, the preregistration is merely a development stage of the final manuscript, thus sparing authors from writing, and editors and reviewers from evaluating two separate documents.

@@

When leaving meta-scientific benefits aside, a preregistration is also a tool for planning a study.
To use PAC for study planning, we suggest that researchers write a dynamically generated manuscript including the sections Introduction, Methods, and Results (or similar) _before_ they gather empirical data.
To that end, they should borrow from widely employed standards for writing an empirical manuscript [e.g. @apa7].
Then they should translate their method section into executable computer code and simulate data that has the same structure as the data they expect to obtain from their experiments.

@@

With simulated data, researchers can check if the analysis recovers the known parameters of the simulation.
When an analysis fails to recover the correct values in idealized conditions with big samples, researchers should not expect this analysis to be effective under realistic conditions.
Because the simulation captures the researchers' expectations about the real world, it is the best way to assess the effectiveness of the analysis without actually gathering the data.

@@

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  # 1. warn users that the results are mocked
  # 2. draw `n` samples with `effect_size`
  # 3. format and return in expected data format
}
```

@@

When the researchers are satisfied with the function `planned_analysis()`, they can think about how they would like to report the analysis results via tables, plots, and text.
The implementation of this reporting should be in the function `report_analysis()`.

```{r, eval=FALSE}
report_analysis <- function(results){
  # 1. create markdown tables from results
  # 2. conditionally interpret results e.g. if(p < .025)"Result is significant."
  # 3. visualize results
  # 4. return results section formatted in markdown
}
```

@@

The interested reader can find the example rendered as a pdf file with actual data in the [online supplementary material](this link does not work) and can view the changes we made since preregistering it on this [GitHub page](this link does not work).

@@

Please note that the statistical procedure in the PAC example of running different test procedures based on a fixed skewness threshold was created for didactic purposes and is not necessarily optimal for addressing your research question.
The t-test and Mann–Whitney–Wilcoxon test are arguably the most often used hypothesis test [@fagerlandTtestsNonparametricTests2012; @hortonStatisticalMethodsJournal2005 reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005].
The analytical strategy presented here is in fact suboptimal with regard to several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions [@stonehouseRobustnessTestsCombined1998]).
